The error in Bayesian phylogenetic inference when speciation is protracted

### 2019-12-17 content.tex
Use new naming

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Methods (but we are not allowed to use this header)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Hypotheses} \richel{but we are not allowed to use this header}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Hypotheses}

$\mathcal{H}_1$: RJCB expects that the inference error is lowest when the true
tree is generated under PBD parameter settings without protractedness, 
i.e $SCR = \infty$. For such parameters settings, the
true tree is in practice generated by a BD model, which
matches the tree prior used in inference. Without a mismatch between
true tree prior and assumed tree prior, this source of errors will be absent,
where the other two sources of errors (stochasticity in the
simulation of the alignment and the MCMC algorithm) 
will remain the same. \richel{figure 1a and b}

$\mathcal{H}_2$: RJCB expects that, on average, the inference error is highest for
parameter settings with a lower speciation rate, 
as for these settings, 
the mismatch between the the speciation model that
generated the true tree (which is profoundly-P PBD) is biggest with
the tree prior assumed to be generative (which is BD). \richel{figure 1a and b}

$\mathcal{H}_3$: RJCB expects that the inference error is higher for true trees
with an observable/actual higher percentage of extant incipient species,
regardless of the PBD parameters.
These incipient species are one of the three (and the most 
interesting) sources of error, as a BD model -as a feature- will never
infer the branch-length distribution of protracted species. \richel{figure 2}

$\mathcal{H}_4$: RJCB expects that, on average, the inference error is equal for
parameter settings with an equal SIRI, SIRG and SCR, i.e. extinction
has no effect on the error made, because extinction affects all species equally. 
\richel{figure 1a and b, or a new figure}

$\mathcal{H}_5$: RJCB expects that an increased number of taxa
has a negative effect on the variance of the errors made, as there
is more information available to base inference on.
\richel{figure 3}

$\mathcal{H}_6$: RJCB expects that an increased extinction rate
increases the variance of the errors made,
due to the decrease of the number of taxa, reducing the amount of information
to base inference on.
\richel{figure 4}

$\mathcal{H}_7$: RJCB expects that the nLTT statistic between a true and twin
tree at the start of the pipeline,
will correlate strongly with the difference
between the highest posterior density (HPD) of the 
errors of the true and twin tree 
generated at the end of the pipeline. 
This hypothesis
stems from the idea of assuming a setup without noise; that is, with
a DNA alignment of infinite length. From such a DNA alignment 
with infinite information, the MCMC
is able to infer the close-to-correct phylogeny.
\richel{if this is true, we can use this shortcut (instead of running
multiple pirouette replicates) to draw stronger conclusions}
\richel{figure 5}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{20191126_nltt_as_proxy.png}
  \caption{
    The nLTT statistic between true and twin tree correlates strongly
    with the difference between (the highest posterior density
    of) the errors of the true and twin tree.
  }
  \label{fig:nltt_as_proxy}
\end{figure}

$\mathcal{H}_8$: RJCB expects that for settings without extinctions,
the candidate model with JC69, strict and Yule will come up as the best
model most, as that model is the generative model, where the HKY, strict, BD
will be seleted least, as both its site and tree model are needlessly complex.
For settings with extinctions, RJCB predict HKY, strict and Yule will come up 
as the worst model mostly, as it uses both an incorrect site model and incorrect
tree model.

$\mathcal{H}_9$: RJCB expects that different ways of sampling have 
no effect.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methods} \richel{but we are not allowed to use this header}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
